CCVPN: Content Centric Virtual Private Networking

### 2016-12-22 paper/main.tex
adding results to paper

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{throughput_pk_1x1}
\caption{Throughput in public key mode}
\label{throughput1x1}
\end{figure}

>>>>

\begin{figure*}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_1x1.png}\label{1a}}
  \hfil
  \subfigure[2 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_2x1.png}\label{1b}}
  \hfil
  \subfigure[3 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_3x1.png}\label{1c}}
  \hfil
  \subfigure[4 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_4x1.png}\label{1d}}
\caption{Throughput per consumer in public key mode. 1 Producer N consumers}\label{exp1}
\end{figure*}

\begin{figure*}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{throughput_pk_1x1.png}\label{2a}}
  \hfil
  \subfigure[2 Consumers x 2 Producers]{\includegraphics[width=1.5in]{throughput_pk_2x2.png}\label{2b}}
  \hfil
  \subfigure[3 Consumers x 3 Producers]{\includegraphics[width=1.5in]{throughput_pk_3x3.png}\label{2c}}
  \hfil
  \subfigure[4 Consumers x 4 Producers]{\includegraphics[width=1.5in]{throughput_pk_4x4.png}\label{2d}}
\caption{Throughput per consumer in public key mode. N Producers N consumers}\label{exp2}
\end{figure*}

\begin{figure*}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_1x1.png}\label{3a}}
  \hfil
  \subfigure[2 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_2x1.png}\label{3b}}
  \hfil
  \subfigure[3 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_3x1.png}\label{3c}}
  \hfil
  \subfigure[4 Consumers x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_4x1.png}\label{3d}}
\caption{Throughput per consumer in symmetric key mode. 1 Producer N consumers}\label{exp3}
\end{figure*}

\begin{figure*}[!t]
\centering
  \subfigure[1 Consumer x 1 Producer]{\includegraphics[width=1.5in]{throughput_sk_1x1.png}\label{4a}}
  \hfil
  \subfigure[2 Consumers x 2 Producers]{\includegraphics[width=1.5in]{throughput_sk_2x2.png}\label{4b}}
  \hfil
  \subfigure[3 Consumers x 3 Producers]{\includegraphics[width=1.5in]{throughput_sk_3x3.png}\label{4c}}
  \hfil
  \subfigure[4 Consumers x 4 Producers]{\includegraphics[width=1.5in]{throughput_sk_4x4.png}\label{4d}}
\caption{Throughput per consumer in symmetric key mode. N Producers N consumers}\label{exp4}
\end{figure*}
